---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# stash

<!-- badges: start -->
[![AppVeyor build status](https://ci.appveyor.com/api/projects/status/github/iqis/stash?branch=master&svg=true)](https://ci.appveyor.com/project/iqis/stash)
[![Travis build status](https://travis-ci.org/iqis/stash.svg?branch=master)](https://travis-ci.org/iqis/stash)
[![Codecov test coverage](https://codecov.io/gh/iqis/stash/branch/master/graph/badge.svg)](https://codecov.io/gh/iqis/stash?branch=master)
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/stash)](https://cran.r-project.org/package=stash)
<!-- badges: end -->

The goal of stash is to ...

## Installation

```{r eval = FALSE}
devtools::install_github("iqis/stash")
```


## Example

```{r include = FALSE}
require(stash)
require(magrittr)
```

Make a stash. 
```{r}
# Make sure the path exists, as right now it would not create one if not found
mtc_stash <- stash(mtcars)
mtc_stash
```

This means that mtcars is written into the above location. It is thus exposed that I use Windows. 


Access the stash's content with `$.`
```{r}
mtc_stash$. %>% head()
```


The object also provides access other useful information.
```{r}
mtc_stash$obj_class
mtc_stash$obj_size
mtc_stash$file_path
mtc_stash$has_stash_file()
mtc_stash$has_content()
```

Currently, as the data set is stashed on to the disc, we don't have a copy in the memory. But we can load it.
```{r}
mtc_stash$has_content()
mtc_stash$load_content()
mtc_stash$has_content()
mtc_stash$.
```

We can also remove the in-memory content to release memory. But we still can read from the disk as in the beginning. 
```{r}
mtc_stash$remove_content()
mtc_stash$has_content()
```

```{r}
mtc_stash$.
```

Finally we can also remove the stash on the disk. If we do this now, we will end with no data anywhere.
```{r error = TRUE}
mtc_stash$remove_stash()
mtc_stash$has_stash_file()
mtc_stash$.
```




